Constant-round Blind Classical Verification of Quantum Sampling

### 2020-07-11 paper.tex
Delete FBQP which was commented out
Add notes and others' updates
Sync with local for macro changes
Sync with local to fix smart quotes
Sync Github and Overleaf

@@

\usepackage{amsmath, amssymb, amsthm}
\usepackage{braket}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage[margin=1in]{geometry}
\newcommand{\sgn}{\operatorname{sgn}}
\DeclareMathOperator*{\E}{\mathbb{E}}
\DeclareMathOperator*{\spn}{\operatorname{span}}
\DeclareMathOperator*{\poly}{\operatorname{poly}}
\newcommand{\norm}[1]{\left\lVert#1\right\rVert}
\usepackage{etoolbox}
\usepackage{hyperref}
\apptocmd{\thebibliography}{\raggedright}{}{}
\usepackage{cite,color,float}
\usepackage{mdframed} 
\usepackage{cleveref}
\crefname{protocol}{protocol}{protocols}
\Crefname{protocol}{Protocol}{Protocols}
\crefname{thm}{theorem}{theorems}
\Crefname{thm}{Theorem}{Theorems}
\crefname{rmk}{remark}{remarks}
\Crefname{rmk}{Remark}{Remarks}
\crefname{lem}{lemma}{lemmata}
\Crefname{lem}{Lemma}{Lemmata}

@@

%\pagecolor{black}
%\color{white}

\newcounter{protocol}
\newcommand{\linefill}{\rule{\linewidth}{0.8pt}}

@@

\newcommand{\KM}[1]{{\footnotesize\color{cyan}[KM: #1]}}
\newcommand{\Ethan}[1]{{\footnotesize\color{magenta}[Ethan: #1]}}
\newcommand{\XW}[1]{{\footnotesize\color{red}[XW: #1]}}

@@

%\iffalse
\author[1]{Kai-Min Chung\thanks{\href{mailto:kmchung@iis.sinica.edu.tw}{kmchung@iis.sinica.edu.tw}. Partially supported by the 2019 Academia Sinica Career Development Award under Grant no. 23-17, and MOST QC project under Grant no. MOST 108-2627-E-002-001.}}
\author[2]{Yi Lee\thanks{\href{mailto:ethanlee515@gmail.com}{ethanlee515@gmail.com}.}}
\author[3]{Han-Hsuan Lin\thanks{\href{mailto:linhh@cs.utexas.edu}{linhh@cs.utexas.edu}.}}
\author[4]{Xiaodi Wu\thanks{\href{mailto:xwu@cs.umd.edu}{xwu@cs.umd.edu}. Partially supported by the U.S. National Science Foundation grant CCF-1755800, CCF-1816695, and CCF-1942837(CAREER).}}
\affil[1, 2]{Institute of Information Science, Academia Sinica, Taiwan}
\affil[3]{Department of Computer Science, University of Texas at Austin, USA}
\affil[4]{
	Department of Computer Science, Institute for Advanced Computer Studies,
	and Joint Center for Quantum Information and Computer Science,
	University of Maryland, USA
}
%\fi
%\author{}
%\institute{}

@@

% \input{fbqp}

@@

\input{qpip}

>>>>

\newif\ifdraft
%\drafttrue
\draftfalse

@@

\usepackage{amsmath, amssymb, amsthm}
\usepackage{stmaryrd}
\usepackage{braket}
\usepackage{algorithm}
\usepackage{enumitem}
\usepackage{algpseudocode}
\usepackage[margin=1in]{geometry}
\newcommand{\sgn}{\operatorname{sgn}}
\DeclareMathOperator*{\E}{\mathbb{E}}
\DeclareMathOperator*{\spn}{\operatorname{span}}
\DeclareMathOperator*{\poly}{\operatorname{poly}}
\newcommand{\norm}[1]{\left\lVert#1\right\rVert}
\usepackage{etoolbox}
\usepackage{hyperref}
\apptocmd{\thebibliography}{\raggedright}{}{}
\usepackage{cite,color,float}
\usepackage{mdframed} 
\usepackage{cleveref}
\crefname{protocol}{protocol}{protocols}
\Crefname{protocol}{Protocol}{Protocols}
\crefname{thm}{theorem}{theorems}
\Crefname{thm}{Theorem}{Theorems}
\crefname{rmk}{remark}{remarks}
\Crefname{rmk}{Remark}{Remarks}
\crefname{lem}{lemma}{lemmata}
\Crefname{lem}{Lemma}{Lemmata}

@@

%\pagecolor{black}
%\color{white}
\numberwithin{equation}{section}
\newcounter{protocol}
\newcommand{\linefill}{\rule{\linewidth}{0.8pt}}

@@

\ifdraft
\newcommand{\KM}[1]{{\footnotesize\color{cyan}[KM: #1]}}
\newcommand{\Ethan}[1]{{\footnotesize\color{magenta}[Ethan: #1]}}
\newcommand{\XW}[1]{{\footnotesize\color{red}[XW: #1]}}
\else
\newcommand{\KM}[1]{}
\newcommand{\Ethan}[1]{}
\newcommand{\XW}[1]{}
\fi

\def \Hin {H_{\mathrm{in}}}
\def \Hout {H_{\mathrm{out}}}
\def \Hprop {H_{\mathrm{prop}}}
\def \Hclock {H_{\mathrm{clock}}}
\def \Jclock {J_{\mathrm{clock}}}
\def \Jprop {J_{\mathrm{prop}}}
\def \Kin {K_{\mathrm{in}}}
\def \Kclock {K_{\mathrm{clock}}}
\def \Kprop {K_{\mathrm{prop}}}

\newcommand{\histpsi}[1]{\ket{\psi_{#1}^{\mathrm{hist}}}}
\newcommand{\LHXZ}[1]{\mathrm{LH}_{\mathrm{XZ}}^{#1}}
\newcommand{\ground}[1]{{\lambda \left (#1 \right)}}

@@

%\iffalse
\author[1]{Kai-Min Chung\thanks{\href{mailto:kmchung@iis.sinica.edu.tw}{kmchung@iis.sinica.edu.tw}. Partially supported by the 2019 Academia Sinica Career Development Award under Grant no. 23-17, and MOST QC project under Grant no. MOST 108-2627-E-002-001.}}
\author[2]{Yi Lee\thanks{\href{mailto:ethanlee515@gmail.com}{ethanlee515@gmail.com}. This work was done in part while the author was affiliated to National Taiwan University.}}
\author[3]{Han-Hsuan Lin\thanks{\href{mailto:linhh@cs.utexas.edu}{linhh@cs.utexas.edu}. Supported by Aaronson's Vannevar Bush Faculty Fellowship from the US Department of Defense.}}
\author[4]{Xiaodi Wu\thanks{\href{mailto:xwu@cs.umd.edu}{xwu@cs.umd.edu}. Partially supported by the U.S. National Science Foundation grant CCF-1755800, CCF-1816695, and CCF-1942837(CAREER).}}
\affil[1, 2]{Institute of Information Science, Academia Sinica, Taiwan}
\affil[3]{Department of Computer Science, University of Texas at Austin, USA}
\affil[4]{
	Department of Computer Science, Institute for Advanced Computer Studies,
	and Joint Center for Quantum Information and Computer Science,
	University of Maryland, USA
}
%\fi
%\author{}
%\institute{}

@@

@@

%\input{qpip}
